FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-02-05 ess_marmo.tex
Update on Overleaf.

\item{\texttt{BLANK}.
This keyword must be used only in integer data.
It contains an integer that specifies the value that is used to
represent pixels that have an undefined physical value.... 
\textit{PDS4 Special\_Constants?}}

@@

\item{\texttt{DATE}.
The date on which the file was created,}
\item{\texttt{DATE-OBS}}
\item{\texttt{INSTRUME}}
\item{\texttt{TELESCOP}}
\item{\texttt{OBJECT}}
\item{\texttt{ORIGIN}}
\item{\texttt{AUTHOR}}
\item{\texttt{REFERENC}}

@@

\bibliography{epss_marmo}

>>>>

\item{\texttt{BLANK}.
This keyword must be used only in integer data.
It contains an integer that specifies the value that is used to
represent pixels that have an undefined physical value.... 
\texttt{PDS4 Special\_Constants?}}

@@

\item{\texttt{DATE}.
It contains the date on which the file was created, provided as ISO 8601
string.
PDS4 provides a \texttt{creation\_date\_time} attribute defining date
and time of product creation.}

\item{\texttt{DATE-OBS}.
It contains the date of the observation, provided as ISO 8601
string. The value shall be assumed to refer to the start of the observation,
unless another interpretation is clearly explained in the comment field.
It is assumed to be expressed in UTC but other systems are accepted as long as they
are specified in the ISO string. 
PDS4 provides a \texttt{Time\_Coordinates} class with attributes
\textit{start\_date\_time} and \texttt{stop\_date\_time} providing start and
stop date and time appropriate to the product being labeled, always in UT
coordinates.
EPN-TAP also strongly recommends to fill in the \texttt{time\_min} and
\texttt{time\_max} fields, always in UTC and formatted in Julian Days.}
% * <chiara.marmo@u-psud.fr> 2018-02-05T10:20:13.335Z:
% 
% > Julian Days
% From https://voparis-confluence.obspm.fr/display/VES/EPN-TAP+v2+parameter+description I see that ISO format is still in the race.... Maybe it would be better to homogenize PDS4 EPN-TAP and FITS?
% 
% ^.

\item{\texttt{INSTRUME}.}
\item{\texttt{TELESCOP}}
\item{\texttt{OBJECT}}
\item{\texttt{ORIGIN}}
\item{\texttt{AUTHOR}}
\item{\texttt{REFERENC}}

@@

\bibliography{ess_marmo}
